Emulation of high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2022-11-02 main.tex
proof read chapter 1

	Research presented in this thesis are based on joint work
	published in the articles:
	\begin{itemize}
		\item Chapter \ref{chapter:fame1} is based on \cite{Maitre:2021uaa}: Daniel Ma\^{i}tre and Henry Truong, \textit{A factorisation-aware Matrix element emulator}, Journal of High Energy Physics, 2021 (11). 066.
		\item Chapter \ref{chapter:fame2} is based on ...
		\item Chapter \ref{chapter:fame3} is based on ...
	\end{itemize}

	Other research projects carried out during my studies but not included
	in this thesis:
	\begin{itemize}
		\item \cite{doi:10.1098/rsos.210506}: J. Aylett-Bullock, C. Cuesta-Lazaro, A. Quera-Bofarull, M. Icaza-Lizaola, A. Sedgewick, H. Truong, A. Curran, E. Elliott, T. Caulfield, K. Fong, I. Vernon, J. Williams, R. Bower and F. Krauss, \textit{June: open-source individual-based epidemiology simulation}, (2021), R. Soc. open sci.8210506210506.
		\item \cite{doi:10.1098/rsta.2022.0039}: I. Vernon, J. Owen, J. Aylett-Bullock, C. Cuesta-Lazaro, J. Frawley, A. Quera-Bofarull, A. Sedgewick, D. Shi, H. Truong, M. Turner, J. Walker, T. Caulfield, K. Fong and F. Krauss, \textit{Bayesian emulation and history matching of JUNE}, (2022), Phil. Trans. R. Soc. A.3802022003920220039.
	\end{itemize}

>>>>

	Research presented in this thesis is based on joint work
	published in the articles:
	\begin{itemize}
		\item Chapter \ref{chapter:fame1} is based on \cite{Maitre:2021uaa}: Daniel Ma\^{i}tre and Henry Truong, \textit{A factorisation-aware Matrix element emulator}, Journal of High Energy Physics, 2021 (11). 066.
		\item Chapter \ref{chapter:fame2} is based on ...
		\item Chapter \ref{chapter:fame3} is based on ...
	\end{itemize}

	Other research projects published during my studies but not included
	in this thesis:
	\begin{itemize}
		\item \cite{doi:10.1098/rsos.210506}: J. Aylett-Bullock, C. Cuesta-Lazaro, A. Quera-Bofarull, M. Icaza-Lizaola, A. Sedgewick, H. Truong, A. Curran, E. Elliott, T. Caulfield, K. Fong, I. Vernon, J. Williams, R. Bower and F. Krauss, \textit{June: open-source individual-based epidemiology simulation}, (2021), R. Soc. open sci.8210506210506.
		\item \cite{doi:10.1098/rsta.2022.0039}: I. Vernon, J. Owen, J. Aylett-Bullock, C. Cuesta-Lazaro, J. Frawley, A. Quera-Bofarull, A. Sedgewick, D. Shi, H. Truong, M. Turner, J. Walker, T. Caulfield, K. Fong and F. Krauss, \textit{Bayesian emulation and history matching of JUNE}, (2022), Phil. Trans. R. Soc. A.3802022003920220039.
	\end{itemize}
